You can mail submissions for the Jargon File to \url{yashtulsyan@gmail.com}.

We welcome new jargon, and corrections to or amplifications of existing entries. You can improve your submission's chances of being
included by adding background information on user population and years of currency. References to actual usage via URLs and/or DejaNews
pointers are particularly welcomed.

All contributions and suggestions about the Jargon File will be considered donations to be placed in the public domain as part of this
File, and may be used in subsequent paper editions. Submissions may be edited for accuracy, clarity and concision.

We are looked to expand the File's range of technical specialties covered. There are doubtless rich veins of jargon yet untapped in the
scientific computing, graphics, and networking hacker communities; also in numerical analysis, computer architectures and VLSI design,
language design, and many other related fields. Send us your jargon!

We are not interested in straight technical terms explained by textbooks or technical dictionaries unless an entry illuminates
`underground' meanings or aspects not covered by official histories. We are also not interested in `joke' entries -- there is a lot of
humor in the file but it most flow naturally out of the explanations of what hackers do and how they think. Furthermore, we will
emphatically reject all entries used to promote a political or religious agenda unless it's justified by a large proportion of hackers
(e.g. the Free Software movement will get into the Jargon File, but libertarianism, which does not account for a majority of hackers, would
not). This is one of the reasons why version 5.0.0 was forked from ESR-2003.

It is OK to submit items of jargon you have originated if they have spread to the point of being used by people who are not personally
acquainted with you. We prefer items to be attested by independent submission from two different sites.

Please send URLs for materials related to the entries, so we can enrich the File's link structure.

The Jargon File will be regularly maintained and made available for browsing on the World Wide Web, and will include a version number. Read
it, pass it around, contribute -- this is your monument!

