Pronunciation keys are provided in the jargon listings for all entries that are
neither dictionary words pronounced as in standard English nor obvious
compounds thereof. Slashes bracket phonetic pronunciations, which are to be
interpreted using the following conventions:

\renewcommand{\labelenumi}{\arabic{enumi}.}
\begin{enumerate}
	\item Syllables are hyphen-separated, except that an accent or back-accent
		follows each accented syllable (the back-accent marks a secondary
		accent in some words of four or more syllables). If no accent is given,
		the word is pronounced with equal accentuation on all syllables (this
		is common for abbreviations).

	\item Consonants are pronounced as in American English. The letter `g' is
		always hard (as in ``got'' rather than ``giant''); `ch' is soft
		(``church'' rather than ``chemist''). The letter `j' is the sound that
		occurs twice in ``judge''. The letter `s' is always as in ``pass'',
		never a z sound. The digraph `kh' is the guttural of ``loch'' or
		``l'chaim''. The digraph `gh' is the aspirated g+h of ``bughouse'' or
		``ragheap'' (rare in English).

	\item Uppercase letters are pronounced as their English letter names; thus
		(for example) /H-L-L/ is equivalent to /aych el el/. /Z/ may be
		pronounced /zee/ or /zed/ depending on your local dialect.
	
	\item Vowels are represented as follows:
		\begin{quote}
			back, that\\
			father, palm (see note)\\
			far, mark\\
			flaw, caught\\
			bake, rain\\
			less, men\\
			easy, ski\\
			their, software\\
			trip, hit\\
			life, sky\\
			block, stock (see note)\\
			flow, sew\\
			loot, through\\
			more, door\\
			out, how\\
			boy, coin\\
			but, some\\
			put, foot\\
			yet, young\\
			few, chew\\
			/oo/ with optional fronting as in `news' (/nooz/ or /nyooz/)
		\end{quote}
\end{enumerate}
\renewcommand{\labelenumi}{\colorbox{shadecolor}{{\sffamily\footnotesize\arabic{enumi}\label{\entrylabel-\theenumi}}}}

The glyph /*/ is used for the `schwa' sound of unstressed or occluded vowels
(the one that is often written with an upside-down `e'). The schwa vowel is
omitted in syllables containing vocalic r, l, m or n; that is, in `kitten' and
`color' would be rendered /kit'n/ and /kuhl'r/, not /kit'*n/ and /kuhl'*r/.

Note that the above table reflects mainly distinctions found in standard
American English (that is, the neutral dialect spoken by TV network announcers
and typical of educated speech in the Upper Midwest, Chicago, Minneapolis/St.
Paul and Philadelphia). However, we separate /o/ from /ah/, which tend to merge
in standard American. This may help readers accustomed to accents resembling
British Received Pronunciation.

The intent of this sceme is to permit as many readers as possible to map the
pronunciations into their local dialect by ignoring some subset of the
distinctions we make. Speakers of British RP, for example, can smash terminal
/r/ and all unstressed vowels. Speakers of many varieties of southern American
will automatically map /o/ to /aw/; and so forth. (Standard American makes a
good reference dialect for this purpose because it has crisp consonants and
more vowel distinctions than other major dialects, and tends to retain
distinctions between unstressed vowels. It also happens to be what your editor
speaks.)

Entries with a pronunciation of '//' are written-only usages. (No, Unix
weenies, this does not mean `pronounce like previous pronunciaton'!)

