\mainentry{candygrammar} n.

A programming-language grammar that is mostly \citeentry{syntactic sugar}; the
term is also a play on `candygram'. \citeentry{COBOL}, Apple's Hypertalk
language, and a lot of the so-called `4GL' database languages share this
property. The usual intent of such designs is that they be as English-like as
possible, on the theory that they will then be easier for unskilled people to
program. This intention comes to grief on the reality that syntax isn't what
makes programming hard; it's the mental effort and organization required to
specify an algorithm precisely that costs. Thus the invariable result is that
`candygrammar' languages are just as difficult to program in as terser ones, and
far more painful for the experienced hacker.

[The overtones from the old Chevy Chase skit on Saturday Night Live should not
be overlooked. This was a ``Jaws'' parody. Someone lurking outside an apartment
door tries all kinds of bogus ways to get the occupant to open up, while ominous
music plays in the background. The last attempt is a half-hearted ``Candygram!''
When the door is opened, a shark bursts in and chomps the poor occupant. [There
is a similar gag in ``Blazing Saddles'' --ESR] There is a moral here for those
attracted to candygrammars. Note that, in many circles, pretty much the same
ones who remember Monty Python sketches, all it takes is the word
``Candygram!'', suitably timed, to get people rolling on the floor.
--\Changes{There was a space after the en dash.}GLS]

