\mainentry{HCF} /H-C-F/ n.

Mnemonic for `Halt and Catch Fire', any of several undocumented and semi-mythical machine instructions with destructive side-effects,
supposedly included for test purposes on several well-known architectures going as far back as the IBM 360. The MC6800 microprocessor was
the first for which an HFC opcode became widely known. This instruction caused the processor to \citeentry{toggle} a subset of the bus
lines as rapidly as it could; in some configurations this could actually cause lines to burn up. Compare \citeentry{killer poke}.

\begin{usenet}
	Once upon a time there was a machine called the Compucolor II. It was made by
	Intecolor, a terminal manufacturer, and was deliberately crippled to keep it
	from competing with their terminals. They apparently were able to save about
	\$50 in hardware by giving the software more control over it, and cutting
	safety margins. The file system required al files be contiguous on disk: when
	you deleted a file it compressed the rest of the disk, using video RAM as a
	temporary buffer. Amusing, maybe. But not a very nice machine.

	OK, if you executed the following BASIC program, the display would vanish, it
	would make weird "singing" noises, and a burned smell would be immediately
	obvious. Turning off the power switch didn't have any effect: you have to 
	pull the plug. Whether it would actually catch fire, I was too chicken to find
	out.

	The program?

	\begin{usenet}
		FOR I = 0 TO 255: OUT 6, I: NEXT I

		Anyone know what this did, really?
	\end{usenet}

	\citeusenet{da Silva, Poster}{unknown}{1989}{Real life HCF code in this message}{alt.folklore.computers}{ZUsgBQklhJ0}{14 December}
\end{usenet}

